\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-08 paper.tex
Minor tuning
Mention the name 'Sally and Ann'

\usepackage{listings}
\usepackage{alltt}
\usepackage{fancyvrb}

@@

One classical application of this cognitive skills is the so-called
\emph{False-Belief} experiment~\cite{Leslie2000}: a child is asked to watch a
scene where two people, A and B, manipulate objects. Then A leaves and B hides
away one object. When A comes back, we ask the child ``where do you think A
will look for the object?''. Before acquiring a theory of mind, children are
not able to separate their own (true) model of the world (where they know that
the object was hidden) from the model of A, which contains \emph{false beliefs}
on the world (A still thinks the object is at its original position since he
did not see B hiding it). Using seperate knowledge models in the knowledge
base, we have been able to replicate this experience on our
robots~\cite{Warnier2012a}.

>>>>

\usepackage{listings}
\usepackage{alltt}
\usepackage{fancyvrb}
\usepackage{flushend} % equalize the column length on last page

@@

One classical application of this cognitive skills is the so-called
\emph{False-Belief} experiment (also known as the \emph{Sally and Ann}
experiment)~\cite{Leslie2000}: a child is asked to watch a scene where two
people, A and B, manipulate objects. Then A leaves and B hides away one
object. When A comes back, we ask the child ``where do you think A will
look for the object?''. Before acquiring a theory of mind, children are not
able to separate their own (true) model of the world (where they know that
the object was hidden) from the model of A, which contains \emph{false
beliefs} on the world (A still thinks the object is at its original
position since he did not see B hiding it). Using seperate knowledge models
in the knowledge base, we have been able to replicate this experience on
our robots~\cite{Warnier2012a}.
